An agent-based model for city networks based on interactions between firms

### 2019-09-25 slides.tex
ucl_template<3

\title{An agent-based model for city networks based on interactions between firms}
\author{J.~Raimbault$^{1,2,3\ast}$ and N. Zdanowska$^{1,3}$\\\medskip
$^{\ast}$\texttt{j.raimbault@ucl.ac.uk}
}

\institute{$^{1}$CASA, UCL\\
$^{2}$UPS CNRS 3611 Complex Systems Institute Paris\\
$^{3}$UMR CNRS 8504 G{\'e}ographie-cit{\'e}s
}

\date{CCS 2019\\
Satellite Simulation models\\
October 2nd 2019
}

>>>>

\title[Agent-based modeling city networks]{An agent-based model for city networks based on interactions between firms}
\author[Raimbault \and Zdanowska]{J.~Raimbault$^{1,2,3\ast}$ \and N. Zdanowska$^{1,3}$\\\medskip
$^{\ast}$\texttt{j.raimbault@ucl.ac.uk}
}

\institute[UCL]{$^{1}$CASA, UCL\\
$^{2}$UPS CNRS 3611 Complex Systems Institute Paris\\
$^{3}$UMR CNRS 8504 G{\'e}ographie-cit{\'e}s
}

\date[2nd October 2019]{CCS 2019\\
Satellite Simulation models\\
October 2nd 2019
}
